\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-04-20 doc/acknowledgments.tex
Add Sloan acknowledgement

The \sw project is open source.
The web app was developed at \texttt{https://github.com/Zooniverse/Lens-Zoo}
while the SWAP analysis software was developed at
\texttt{https://github.com/drphilmarshall/SpaceWarps}.

>>>>

The \sw project is open source.
The web app was developed at \texttt{https://github.com/Zooniverse/Lens-Zoo}, and was supported by a grant from the Alfred P. Sloan Foundation, 
while the SWAP analysis software was developed at
\texttt{https://github.com/drphilmarshall/SpaceWarps}.
